% Resume 2.0 (2009-04-12)
% Copyright 2009 Zach Scrivena
% zachscrivena@gmail.com
% http://zs.freeshell.org/latexresume/
%
% This document is released under the
% Creative Commons Attribution 3.0 Unported License
% http://creativecommons.org/licenses/by/3.0/

%%%%%%%%%%%%%%
%% PREAMBLE %%
%%%%%%%%%%%%%%

\documentclass[letterpaper,10pt,oneside]{article}
%\documentclass[a4paper,12pt,oneside]{article}
\usepackage{ifthen}
\usepackage{longtable}
\usepackage{setspace}
\usepackage[left=.8in,right=.8in,top=.6in,bottom=0.6in,nohead,nofoot]{geometry}
\usepackage{marvosym}
\usepackage{times}

\usepackage[bookmarks,
pdftitle={Resume},
pdfauthor={Angel Billy Phillips},
pdfsubject={},
pdfcreator={},
pdfproducer={},
pdfkeywords={},
pdfpagemode={},
pdfstartview=FitH,
colorlinks=true,
linkcolor=black,   %Color for normal internal links.
anchorcolor=black, %Color for anchor text.
citecolor=green,   %Color for bibliographical citations in text.
filecolor=magenta, %Color for URLs which open local files.
menucolor=red,     %Color for Acrobat menu items.
urlcolor=black]{hyperref}

\newcommand{\longmonth}[1]{%
\ifthenelse{\equal{#1}{1}}{January}{}%
\ifthenelse{\equal{#1}{2}}{February}{}%
\ifthenelse{\equal{#1}{3}}{March}{}%
\ifthenelse{\equal{#1}{4}}{April}{}%
\ifthenelse{\equal{#1}{5}}{May}{}%
\ifthenelse{\equal{#1}{6}}{June}{}%
\ifthenelse{\equal{#1}{7}}{July}{}%
\ifthenelse{\equal{#1}{8}}{August}{}%
\ifthenelse{\equal{#1}{9}}{September}{}%
\ifthenelse{\equal{#1}{01}}{January}{}%
\ifthenelse{\equal{#1}{02}}{February}{}%
\ifthenelse{\equal{#1}{03}}{March}{}%
\ifthenelse{\equal{#1}{04}}{April}{}%
\ifthenelse{\equal{#1}{05}}{May}{}%
\ifthenelse{\equal{#1}{06}}{June}{}%
\ifthenelse{\equal{#1}{07}}{July}{}%
\ifthenelse{\equal{#1}{08}}{August}{}%
\ifthenelse{\equal{#1}{09}}{September}{}%
\ifthenelse{\equal{#1}{10}}{October}{}%
\ifthenelse{\equal{#1}{11}}{November}{}%
\ifthenelse{\equal{#1}{12}}{December}{}}

\newcommand{\shortmonth}[1]{%
\ifthenelse{\equal{#1}{1}}{Jan}{}%
\ifthenelse{\equal{#1}{2}}{Feb}{}%
\ifthenelse{\equal{#1}{3}}{Mar}{}%
\ifthenelse{\equal{#1}{4}}{Apr}{}%
\ifthenelse{\equal{#1}{5}}{May}{}%
\ifthenelse{\equal{#1}{6}}{Jun}{}%
\ifthenelse{\equal{#1}{7}}{Jul}{}%
\ifthenelse{\equal{#1}{8}}{Aug}{}%
\ifthenelse{\equal{#1}{9}}{Sep}{}%
\ifthenelse{\equal{#1}{01}}{Jan}{}%
\ifthenelse{\equal{#1}{02}}{Feb}{}%
\ifthenelse{\equal{#1}{03}}{Mar}{}%
\ifthenelse{\equal{#1}{04}}{Apr}{}%
\ifthenelse{\equal{#1}{05}}{May}{}%
\ifthenelse{\equal{#1}{06}}{Jun}{}%
\ifthenelse{\equal{#1}{07}}{Jul}{}%
\ifthenelse{\equal{#1}{08}}{Aug}{}%
\ifthenelse{\equal{#1}{09}}{Sep}{}%
\ifthenelse{\equal{#1}{10}}{Oct}{}%
\ifthenelse{\equal{#1}{11}}{Nov}{}%
\ifthenelse{\equal{#1}{12}}{Dec}{}}

% Style settings
\pagestyle{empty}
\setlength{\parindent}{0in}
\renewcommand{\thefootnote}{\fnsymbol{footnote}} % change footnote symbols

% Macros
\newenvironment{myresume}[2]{\pdfbookmark{#1}{#1}{\LARGE{#1}}\vspace{1mm}\hrule\vspace{-3mm}\begin{longtable}{p{0.12\textwidth} p{0.83\textwidth}}~&#2}{\end{longtable}}
\renewcommand{\section}[2]{\vspace{-1.3em}\\\pdfbookmark{#1}{#2}{\singlespace\textsc{#1}}&}
\newcommand{\firstentry}[1]{\newline#1}
\newcommand{\entry}[1]{\vspace{-0.8em}\\~&#1}
\newcommand{\hide}[1]{}

% Datestamp format: \datestamp{YEAR}{MONTH}{DAY}
%\newcommand{\datestamp}[3]{\longmonth{#2} #3, #1}
%\newcommand{\datestamp}[3]{\shortmonth{#2} #3, #1}
\newcommand{\datestamp}[3]{\shortmonth{#2} #1}

%%%%%%%%%%%%%%%%
%% NAME BLOCK %%
%%%%%%%%%%%%%%%%

\begin{document}
\begin{myresume}{Angel Phillips}{\small
Residencial Ana Luc\'ia                 \hfill (506) 8854-1159 \Mobilefone \newline
El Guarco, Cartago \hfill (506) 2592-3753 \Telefon \newline
Costa Rica                             \hfill \href{mailto:bill9889@gmail.com}{\textit{bill9889@gmail.com}} \Letter
}

%%%%%%%%%%%%%%%
%% INTEREST  %%
%%%%%%%%%%%%%%%

\section{Interest}{interest}

\firstentry{
Embedded Systems, Computer Architecture, Digital Signal Processing, Digital Image Processing, Computer Vision, Digital Communications.\newline
}

%%%%%%%%%%%%%%%
%% EDUCATION %%
%%%%%%%%%%%%%%%

\section{Education}{education}

\firstentry{
\href{http://www.tec.cr/}{\textbf{Costa Rica Institute of Technology}}, Cartago, Costa Rica. \newline
Graduate in \href{http://www.ie.itcr.ac.cr/}{Electronics Engineering.} \hfill \datestamp{2008}{02}{15} -- \datestamp{2014}{06}{15} \newline
}

%%%%%%%%%%%%%%%%%%%%%%%%%
%% RESEARCH EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Research \newline Experience}{research}

\firstentry{
\href{http://www.tec.cr/}{\textbf{Costa Rica Institute of Technology}}, Cartago, Costa Rica. \newline
Undergraduate Research Student, Signal and Image Processing Laboratory \hfill \datestamp{2014}{02}{15} -- \datestamp{2014}{06}{15} \newline
Professor Ing. Jorge Castro God\'inez \newline
{\small \textit{Investigation into the relation with vision embedded and performance analysis of the video processor.}}}

\entry{
\href{http://www.tec.cr/}{\textbf{Costa Rica Institute of Technology}}, Cartago, Costa Rica. \newline
Undergraduate Research Student, Research Center in Housing and Construction \hfill \datestamp{2013}{05}{15} -- \datestamp{2013}{11}{15} \newline
Professors  M.B.A Giannina Ortiz Quesada and Ing. Francisco Navarro Henríquez, M.Sc., MBA. \newline
{\small \textit{Structural Monitoring in the bridges with optical sensors network.}}
}

%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACADEMIC EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Academic\newline Experience}{academic}

\firstentry{
\textbf{Graduation Project}, Implementation and evaluation of an algorithm for detecting objects in the multi-core SoC BF609 of Analog. \newline
{\small \textit{The project consist to develop the detecting objects algorithm in the BF609 processor and perform to analysis your performance.}}
}

\entry{
\textbf{Electrical Communications}, The Digital Modulator in FSK. \newline
{\small \textit{The project was implemented in FPGA with the develop of the Direct Digital Synthesis in Verilog.}}
}

\entry{
\textbf{Automatic Control}, Levitation System Adjustable. \newline
{\small \textit{It was implemented with PID controller of adjustable reference in the PSoC Express.}}
}

\entry{
\textbf{Embedded Systems}, MP3 Player in Beagleboard-xM. \newline
{\small \textit{This project was performed with the GStreamer libraries in the Angstrom distribution}}
}

\entry{
\textbf{Embedded Systems}, Security Log with Kinect in Beagleboard-xM. \newline
{\small \textit{This project consist the check the persons in the room and save in security log. It was developed with the OpenKinect Libraries.}}
}

\entry{
\textbf{Digital Systems}, Trigonometric Calculator in FPGA. \newline
{\small \textit{This project consist to compute trigonometric functions with CORDIC algorithm, it was implemented in FPGA with interface communication to the x86 microprocessor.}}
}

\entry{
\textbf{Digital Signal Processing}, Voice synthesizer.\newline
{\small \textit{This project consist to change voice tone with modification the harmonics the voice itself, it was programed in Octave.}}
}
%%%%%%%%%%%%%%%%%%
%% PUBLICATIONS %%
%%%%%%%%%%%%%%%%%%


%\section{Publications}{publications}

%\firstentry{\href{http://www.example.com}
%{J.~Doe, J.~Citizen, and A.~Yone, ``On lasers and global warming,'' in \textit{Proc. Laser Conference}, Las Vegas, Jan. 2007.}}

%\entry{\href{http://www.example.com}
%{J.~Doe and J.~Citizen, ``Effects of Global Warming,'' in \textit{Proc. Laser Symposium}, Baltimore, Oct. 2005.}}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACADEMIC HONORS & AWARDS %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\section{Academic \newline Honors~\& \newline Awards}{honors}

%\firstentry{Dean's List, Fall 2001 through Spring 2005 \hfill \datestamp{2001}{}{} -- \datestamp{2005}{}{} \newline
%{\small For attaining a semester GPA of at least 3.75.}
%}

\iffalse

\entry{Undergraduate Researcher Award, First Engineering University \hfill \datestamp{2005}{05}{15} \newline
{\small For outstanding scientific contributions in the fields of lasers and global-warming.}
}

\entry{International Science Scholarship, Global Science Foundation \hfill \datestamp{2005}{03}{10} \newline
{\small Provides full sponsorship with stipend for undergraduate studies. One of 42 awardees in the world.}
}

\fi
%%%%%%%%%%%%%%%%%%
%% OTHER AWARDS %%
%%%%%%%%%%%%%%%%%%

%\section{Other \newline Honors \& \newline Awards}{otherhonors}

%\firstentry{Chess Tournament, First Prize, First Engineering College \hfill \datestamp{2004}{03}{10} \newline
%{\small Awarded at the Tenth Annual Chess Tournament held during Alumni Weekend.}
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% CAMPUS ACTIVITIES & POSITIONS HELD %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%\section{Campus \newline Activities~\& \newline Positions \newline Held}{activities}

%%\firstentry{
%%{\textbf{First Volunteers Club}, First Engineering University} \newline
%%President \hfill \datestamp{2004}{01}{20} -- \datestamp{2005}{01}{20} \newline
%%{\small Lorem ipsum dolor sit amet, consectetuer adipiscing elit. Curabitur quam ante, elementum et, dapibus et, porta in, ante. Morbi hendrerit orci sed sem. Fusce est ante, consequat ut, condimentum pellentesque, eleifend at, risus. Curabitur arcu. Sed fermentum ullamcorper diam. Vivamus rhoncus nunc vitae tellus. Sed feugiat mattis urna.}
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% OTHER WORK EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\section{Other~Work \newline Experience}{work}

%\firstentry{
%{\textbf{Alpha Engineering Firm}, Oakland, Ohio} \newline
%Project Officer, Research \& Development Division \hfill \datestamp{2004}{06}{01} -- \datestamp{2005}{05}{31} \newline
%{\small Lorem ipsum dolor sit amet, consectetuer adipiscing elit. Curabitur quam ante, elementum et, dapibus et, porta in, ante. Morbi hendrerit orci sed sem. Fusce est ante, consequat ut, condimentum pellentesque, eleifend at, risus. Curabitur arcu. Sed fermentum ullamcorper diam. Vivamus rhoncus nunc vitae tellus. Sed feugiat mattis urna.}
%}

%%%%%%%%%%%%%%%%%%%%%%
%% TECHNICAL SKILLS %%
%%%%%%%%%%%%%%%%%%%%%%

\section{Technical skills}{skills}

\firstentry{
\textbf{Programming and Scripting Languages:} C/C++, Python, Java, Assembly (IA-32, Microchip), Matlab/Octave. \newline
}
\entry{
\textbf{Hardware Description Language:} Verilog, VHDL. \newline
}
\entry{
\textbf{Tools:} \LaTeX, Subversion, LabView, Xilinx ISE, Altera Quartus, ModelSim, PSoCCreator, Visual Studio, Matlab/Octave, OpenCV, OpenKinect, CrossCore Embedded Studio, PSpice. \newline
}
\entry{
\textbf{Operating Systems:} Windows, Linux. \newline
}
\entry{
\textbf{Embedded Systems and Microprocessors:} Embedded Vision Starter Kit, PSoC® Development Kit, Open hardware systems, FPGA Development Kit, dsPIC, PIC16/18. \newline
}
%%%%%%%%%%%%%%%
%% LANGUAGES %%
%%%%%%%%%%%%%%%

\section{Languages}{languages}

\firstentry{
Spanish (native), English (intermedia).
}
%%%%%%%%%%%%%%%%%
%% SOFT SKILLS %%
%%%%%%%%%%%%%%%%%

\section{Soft skills}{skills}

\firstentry{
Leadership, work in groups, teach to others, active listening, decision making, delegate, work through accomplishments and goals oriented.
}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% EXTRACURRICULAR ACTIVITIES %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Others\newline Activities}{other activities}

\firstentry{
Musical Composition, Independent drummer, Volunteering, Soccer player, Camping in the mountain.
}

%%%%%%%%%%%%%%%
%% REFERENCE %%
%%%%%%%%%%%%%%%

\section{References}{references}

\firstentry{
Ing. Jorge Castro God\'inez \newline jocastro@itcr.ac.cr \Letter \newline Electronics Engineering School \newline Costa Rica Institute of Technology \newline (506) 2550-9231 \Telefon \newline 


Ing. Johan Carvajal God\'inez \newline johcarvajal@itcr.ac.cr \Letter \newline Electronics Engineering School \newline Costa Rica Institute of Technology \newline (506) 2550-9171 \Telefon \newline 


Bach. Olga Ortega Navarro \newline oortega318@gmail.com \Letter \newline Administration Technical \newline Costa Rican Social Security \newline (506) 2573-7575 \Telefon 
}
\end{myresume}
\end{document}